Commit Rater

### 2015-08-26 presentations/paper/methodology.tex
Add analysis header in paper

\subsubsection{no\_vulgarity}
\footnote{This criterion may or may not have been inspired by \url{http://www.commitlogsfromlastnight.com/}}
\label{subs:no_vulgarity}
A commit message should obviously not contain any vulgarity for many reasons, but it should suffice to say that such things are unprofessional and will rarely make the commit any better.

@@

>>>>

\subsubsection{no\_vulgarity}
\label{subs:no_vulgarity}
A commit message should obviously not contain any vulgarity for many reasons, but it should suffice to say that such things are unprofessional and will rarely make the commit any better.

@@

Under the assumption that our synthesis results are metrics for the ``goodness'' of commits, we need to analyse them in order to aggregate a measure of ``goodness''. This analysis can be performed on three levels:

\begin{itemize}
  \item Per commit-level: Analysis could be done on the results of checking an individual commit against our criteria.
  \item Per author-level: This level would aggregate the metrics for all commits of an author in a repository and create a rating of the authors commit behaviour.
  \item Per repository-level: This level would aggregate the metrics of all authors in a repository and create a ranking for the whole team.
\end{itemize}

On each level, it is furthermore possible to analyse either the results of all criteria-checks or only the check/checks for one criterion. These six possibilities will be discussed below.

% 1. Level: No use
% 2. Level: Commit Rater Web
% 3: Level: Boxplots
